`r params$doc_title`

### 2022-12-22 scripts/MSc.Rmd
calculated performance metrics for both GSD and GBC

## Simulation

We simulate

@@

### Performance Metrics

```{r calculate-performance-metrics}
# fns
bias <- function(thetaobs,theta, ...) mean(thetaobs)- theta
mse <- function(thetaobs, theta, ...) mean((thetaobs-theta)^2)
emp_se <- function(nsim, thetaobs, theta, ...) sqrt( 1/(nsim-1) * sum((thetaobs-mean(thetaobs))^2) )  # == sd

colname_theta <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "theta_sim")]
colname_theta_se <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "theta_se_sim")]
colname_pve_X <-  colnames(est_sim)[str_detect(colnames(est_sim), pattern = "pve_X_sim")]
colname_pve_Y <-  colnames(est_sim)[str_detect(colnames(est_sim), pattern = "pve_Y_sim")]

# filter out sample sizes
sample_size_filtered <- as.numeric(str_extract(colname_theta, pattern = "(\\d)+"))

## get performance metrics    # https://stackoverflow.com/questions/47415072/pass-multiple-functions-to-purrrmap
funs <- c(mean = mean, bias = bias, mse = mse, emp_se=emp_se)
args <- list(theta = est$estimate[est$mr_methods == "conmix"], nsim=nrow(est_sim)) # trim argument non-matching and ignored for median

performance_metrics <- est_sim %>% 
  select(!!!(colname_theta)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)

# est_sim %>%    # equivalent to `emp_se()` function, but `sd()` misses dotdotdot argument 
#   select(!!!(colname_theta)) %>% 
#   map_dbl(.f = ~sd(.))
```

```{r further-metrics}
# coverage
coverage <- function(thetaobs, thetaobs_se, theta, ...) {
  lower_ci <- thetaobs - thetaobs_se
  upper_ci <- thetaobs + thetaobs_se
  coverage <- mean(lower_ci <= theta & upper_ci >= theta)
  return(coverage)
}
coverage_bias_eliminated <- function(thetaobs, thetaobs_se, ...) {
  lower_ci <- thetaobs - thetaobs_se
  upper_ci <- thetaobs + thetaobs_se
  mean_thetaobs <- mean(thetaobs)
  coverage_bias_eliminated <- mean(lower_ci <= mean_thetaobs & upper_ci >=mean_thetaobs)
  return(coverage_bias_eliminated)
}

type1error <- function(pvals) sum(pvals<=0.05)/length(pvals)  # no causal_effect

coverage_calc <- c()
coverage_bias_eliminated_calc <- c()
type1error_calc <- c()
for (i in 1:length(sample_size_filtered)) {
  sample_size <- sample_size_filtered[i]
  col_theta <- paste0("theta_sim_", format(sample_size, scientific = FALSE))
  col_theta_se <- paste0("theta_se_sim_", format(sample_size, scientific = FALSE))
  col_mr_pval <- paste0("mr_pval_", format(sample_size, scientific = FALSE))

  coverage_calc[i] <- coverage(thetaobs = est_sim[col_theta], thetaobs_se = est_sim[col_theta_se], theta = est$estimate[est$mr_methods == "conmix"])
  coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_theta]], thetaobs_se = est_sim[[col_theta_se]])
  type1error_calc[i] <- type1error(est_sim[[col_mr_pval]])
}

performance_metrics <- performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(coverage_calc, coverage_bias_eliminated_calc, type1error_calc)) %>% 
  as_tibble()
```

### Performance plots

@@

@@

boxplot_overlay_dat <- pve_X_sim %>% 
  cbind(pve_Y_sim %>% select(-sample_size_filtered)) %>% 
  as_tibble()

## plot
ggplot(plot_data1b, aes(x=n, y=value, col=name))+    # plot_data1b from section Simlating on empirical data (PVE)
  geom_point(alpha=0.6)+
  geom_line(alpha=0.6)+
  geom_line(aes(x=n, y=count_IVs_scaled, col="Number of IVs"), linetype="dotdash")+
  scale_x_continuous(name = paste0("Size of sample ", as.roman(1)),  # 2-sample-MR or label "Study Size"
                     labels = comma, 
                     breaks = N_annotation, #c( 10000, n[7:length(n)]),
                     limits = c(10000, 300000))+
  #ylab("% variance explained by IVs")+
  labs(title = "PVE with simulation added",
       col='', 
       caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       ) +
  scale_y_continuous(
    # Features of the first axis
    name = "% variance explained by IVs",
    # Add a second axis and specify its features
    sec.axis = sec_axis(~./scale_factor, name="Number of IVs"),
    limits = c(0,10)
  ) + 
  #geom_boxplot(data=boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, group=sample_size_filtered))
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2)+
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_Y*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[4,2][[1]],
               alpha=0.2, size=0.2)+
  theme_few()+
  #scale_colour_few() +
  #scale_color_manual(name = "", values = c("% var(U)" = "red", 
  #                                         "% var(X)" = "blue", 
  #                                         "% var(Y)" = "darkblue", 
  #                                         "Number of IVs" = "black"
  #                                         ))
  #
  scale_color_manual(name = "", values = c("% var(U)" = ggthemes_data$few$colors$Dark[2,2][[1]], 
                                           "% var(X)" = ggthemes_data$few$colors$Dark[3,2][[1]], 
                                           "% var(Y)" = ggthemes_data$few$colors$Dark[4,2][[1]], 
                                           "Number of IVs" = "black"),
                     # order
                     breaks = c( "Number of IVs", "% var(X)", "% var(Y)", "% var(U)")
  ) -> plot_pve_simulated
plot_pve_simulated

@@

@@

>>>>

# Simulation

We simulate betas from a normal distribution. The script is outsourced to `simstudy.R`.

@@

## PVE with simulated data Plot

@@

est_sim %>% 
  select(!!!(colname_pve_U)) %>% 
  pivot_longer(everything(), names_to = "PVE_U", values_to = "value_U") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_U_sim

@@

boxplot_overlay_dat <- pve_X_sim %>% 
  cbind(pve_U_sim %>% select(-sample_size_filtered)) %>% 
  cbind(pve_Y_sim %>% select(-sample_size_filtered)) %>% 
  as_tibble()

## plot
ggplot(plot_data1b, aes(x=n, y=value, col=name))+    # plot_data1b from section Simlating on empirical data (PVE)
  geom_point(alpha=0.6)+
  geom_line(alpha=0.6)+
  geom_line(aes(x=n, y=count_IVs_scaled, col="Number of IVs"), linetype="dotdash")+
  scale_x_continuous(name = paste0("Size of sample ", as.roman(1)),  # 2-sample-MR or label "Study Size"
                     labels = comma, 
                     breaks = N_annotation, #c( 10000, n[7:length(n)]),
                     limits = c(10000, 300000))+
  #ylab("% variance explained by IVs")+
  labs(title = "PVE with simulation added",
       col='', 
       caption = "Relationship between sample size, average number of instrumental variables (IVs) and variance of traits explained by the IVs"
       ) +
  scale_y_continuous(
    # Features of the first axis
    name = "% variance explained by IVs",
    # Add a second axis and specify its features
    sec.axis = sec_axis(~./scale_factor, name="Number of IVs"),
    limits = c(0,10)
  ) + 
  #geom_boxplot(data=boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, group=sample_size_filtered))
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_X*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[3,2][[1]],
               alpha=0.2, size=0.2)+
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_U*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[2,2][[1]],
               alpha=0.2, size=0.2)+
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_Y*100, # *100 to get percent values
                                group=sample_size_filtered), 
               col=ggthemes_data$few$colors$Dark[4,2][[1]],
               alpha=0.2, size=0.2)+
  theme_few()+
  #scale_colour_few() +
  #scale_color_manual(name = "", values = c("% var(U)" = "red", 
  #                                         "% var(X)" = "blue", 
  #                                         "% var(Y)" = "darkblue", 
  #                                         "Number of IVs" = "black"
  #                                         ))
  #
  scale_color_manual(name = "", values = c("% var(U)" = ggthemes_data$few$colors$Dark[2,2][[1]], 
                                           "% var(X)" = ggthemes_data$few$colors$Dark[3,2][[1]], 
                                           "% var(Y)" = ggthemes_data$few$colors$Dark[4,2][[1]], 
                                           "Number of IVs" = "black"),
                     # order
                     breaks = c( "Number of IVs", "% var(X)", "% var(Y)", "% var(U)")
  ) -> plot_pve_simulated
plot_pve_simulated

@@

  # confounder simulation
  geom_boxplot(data = boxplot_overlay_dat, aes(x=sample_size_filtered, y=value_U*100, # *100 to get percent values
               col=ggthemes_data$few$colors$Dark[2,2][[1]],
  ggdist::stat_halfeye(data = boxplot_overlay_dat, mapping=aes(x=sample_size_filtered, y=value_U*100, group=sample_size_filtered), 
                       slab_fill=ggthemes_data$few$colors$Dark[2,2][[1]], slab_alpha = 0.2,
    data = boxplot_overlay_dat, mapping=aes(x=sample_size_filtered-2000, y=value_U*100, group=sample_size_filtered), 
    inherit.aes = FALSE, size=0.2, colour=ggthemes_data$few$colors$Dark[2,2][[1]],

@@

## Performance Metrics BIAS, MSE, MEAN, EMP_SE

```{r calculate-performance-metrics}
# fns
bias <- function(thetaobs,theta, ...) mean(thetaobs)- theta
mse <- function(thetaobs, theta, ...) mean((thetaobs-theta)^2)
emp_se <- function(nsim, thetaobs, theta, ...) sqrt( 1/(nsim-1) * sum((thetaobs-mean(thetaobs))^2) )  # == sd (with ...)

# retrieve PVE colnames
colname_pve_X <-  colnames(est_sim)[str_detect(colnames(est_sim), pattern = "pve_X_sim")]
colname_pve_U <-  colnames(est_sim)[str_detect(colnames(est_sim), pattern = "pve_U_sim")]
colname_pve_Y <-  colnames(est_sim)[str_detect(colnames(est_sim), pattern = "pve_Y_sim")]
# retrieve IVW/ MODE/ CONMIX cols for BMI -> GSD
colname_IVW_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_sim_BMI_GSD_")]
colname_IVW_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_se_sim_BMI_GSD_")]
colname_MODE_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_sim_BMI_GSD_")]
colname_MODE_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_se_sim_BMI_GSD_")]
colname_CONMIX_theta_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_sim_BMI_GSD_")]
colname_CONMIX_theta_se_sim_BMI_GSD <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_se_sim_BMI_GSD_")]
# retrieve IVW/ MODE/ CONMIX cols for BMI -> GBC
colname_IVW_theta_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_sim_BMI_GBC_")]
colname_IVW_theta_se_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "IVW_theta_se_sim_BMI_GBC_")]
colname_MODE_theta_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_sim_BMI_GBC_")]
colname_MODE_theta_se_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "MODE_theta_se_sim_BMI_GBC_")]
colname_CONMIX_theta_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_sim_BMI_GBC_")]
colname_CONMIX_theta_se_sim_BMI_GBC <- colnames(est_sim)[str_detect(colnames(est_sim), pattern = "CONMIX_theta_se_sim_BMI_GBC_")]

# filter out sample sizes (IVW only used as example, could be any other col)
sample_size_filtered <- as.numeric(str_extract(colname_IVW_theta_sim_BMI_GSD, pattern = "(\\d)+"))

## get performance metrics    # https://stackoverflow.com/questions/47415072/pass-multiple-functions-to-purrrmap
funs <- c(mean = mean, emp_se=emp_se, bias = bias, mse = mse)
## args gsd
args.gsd.ivw <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "IVW"], 
                     nsim=nrow(est_sim)
                     ) # trim argument non-matching and ignored for median
args.gsd.mode <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "mode"], 
                     nsim=nrow(est_sim)
                     )
args.gsd.conmix <- list(theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "conmix"], 
                     nsim=nrow(est_sim)
                     )
## args gbc
args.gbc.ivw <- list(theta = est$estimate[est$mr_methods == "IVW"], 
                     nsim=nrow(est_sim)
                     ) 
args.gbc.mode <- list(theta = est$estimate[est$mr_methods == "mode"], 
                     nsim=nrow(est_sim)
                     )
args.gbc.conmix <- list(theta = est$estimate[est$mr_methods == "conmix"], 
                     nsim=nrow(est_sim)
                     )
## Standard Deviation
# est_sim %>%    # equivalent to `emp_se()` function, but `sd()` misses dotdotdot argument 
#   select(!!!(colname_theta)) %>% 
#   map_dbl(.f = ~sd(.))
```

```{r CALC-perf-metrics-GSD}
IVW_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_IVW_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.ivw), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)

MODE_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_MODE_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.mode), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)

CONMIX_GSD_performance_metrics <- est_sim %>% 
  select(!!!(colname_CONMIX_theta_sim_BMI_GSD)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gsd.conmix), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
```

```{r CALC-perf-metrics-GBC}
IVW_GBC_performance_metrics <- est_sim %>% 
  select(!!!(colname_IVW_theta_sim_BMI_GBC)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gbc.ivw), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)

MODE_GBC_performance_metrics <- est_sim %>% 
  select(!!!(colname_MODE_theta_sim_BMI_GBC)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gbc.mode), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)

CONMIX_GBC_performance_metrics <- est_sim %>% 
  select(!!!(colname_CONMIX_theta_sim_BMI_GBC)) %>% 
  map_df(.f = ~ funs %>% 
           map(exec, .x, !!!args.gbc.conmix), .id = "var") %>% 
  cbind(sample_size_filtered) %>% 
  rename(N = sample_size_filtered)
```

## Performance Metrics COVERAGE, COVERAGE-BIAS-ELIMINATED, TYPE1ERROR

```{r further-metrics}
# coverage
coverage <- function(thetaobs, thetaobs_se, theta, ...) {
  lower_ci <- thetaobs - thetaobs_se
  upper_ci <- thetaobs + thetaobs_se
  coverage <- mean(lower_ci <= theta & upper_ci >= theta)
  return(coverage)
}
# coverage bias eliminated
coverage_bias_eliminated <- function(thetaobs, thetaobs_se, ...) {
  lower_ci <- thetaobs - thetaobs_se
  upper_ci <- thetaobs + thetaobs_se
  mean_thetaobs <- mean(thetaobs)
  coverage_bias_eliminated <- mean(lower_ci <= mean_thetaobs & upper_ci >=mean_thetaobs)
  return(coverage_bias_eliminated)
}
# type1error
type1error <- function(pvals) sum(pvals<=0.05)/length(pvals)  # no causal_effect

# GSD
IVW_GSD_coverage_calc <- c()
IVW_GSD_coverage_bias_eliminated_calc <- c()
IVW_GSD_type1error_calc <- c()
MODE_GSD_coverage_calc <- c()
MODE_GSD_coverage_bias_eliminated_calc <- c()
MODE_GSD_type1error_calc <- c()
CONMIX_GSD_coverage_calc <- c()
CONMIX_GSD_coverage_bias_eliminated_calc <- c()
CONMIX_GSD_type1error_calc <- c()
# GBC
IVW_GBC_coverage_calc <- c()
IVW_GBC_coverage_bias_eliminated_calc <- c()
IVW_GBC_type1error_calc <- c()
MODE_GBC_coverage_calc <- c()
MODE_GBC_coverage_bias_eliminated_calc <- c()
MODE_GBC_type1error_calc <- c()
CONMIX_GBC_coverage_calc <- c()
CONMIX_GBC_coverage_bias_eliminated_calc <- c()
CONMIX_GBC_type1error_calc <- c()
for (i in 1:length(sample_size_filtered)) {
  sample_size <- sample_size_filtered[i]
  ## GSD additional metrics ----------------------------------------------------
  # IVW
  col_IVW_GSD_theta <- paste0("IVW_theta_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_IVW_GSD_theta_se <- paste0("IVW_theta_se_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_IVW_GSD_mr_pval <- paste0("IVW_mr_pval_BMI_GSD_", format(sample_size, scientific = FALSE))
  # calc
  IVW_GSD_coverage_calc[i] <- coverage(thetaobs = est_sim[col_IVW_GSD_theta], thetaobs_se = est_sim[col_IVW_GSD_theta_se], theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "IVW"])
  IVW_GSD_coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_IVW_GSD_theta]], thetaobs_se = est_sim[[col_IVW_GSD_theta_se]])
  IVW_GSD_type1error_calc[i] <- type1error(est_sim[[col_IVW_GSD_mr_pval]])
  # MODE
  col_MODE_GSD_theta <- paste0("MODE_theta_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_MODE_GSD_theta_se <- paste0("MODE_theta_se_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_MODE_GSD_mr_pval <- paste0("MODE_mr_pval_BMI_GSD_", format(sample_size, scientific = FALSE))
  # calc
  MODE_GSD_coverage_calc[i] <- coverage(thetaobs = est_sim[col_MODE_GSD_theta], 
                                       thetaobs_se = est_sim[col_MODE_GSD_theta_se], 
                                       theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "mode"])
  MODE_GSD_coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_MODE_GSD_theta]], 
                                                                       thetaobs_se = est_sim[[col_MODE_GSD_theta_se]])
  MODE_GSD_type1error_calc[i] <- type1error(est_sim[[col_MODE_GSD_mr_pval]])
  # CONMIX
  col_CONMIX_GSD_theta <- paste0("CONMIX_theta_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_CONMIX_GSD_theta_se <- paste0("CONMIX_theta_se_sim_BMI_GSD_", format(sample_size, scientific = FALSE))
  col_CONMIX_GSD_mr_pval <- paste0("CONMIX_mr_pval_BMI_GSD_", format(sample_size, scientific = FALSE))
  # calc
  CONMIX_GSD_coverage_calc[i] <- coverage(thetaobs = est_sim[col_CONMIX_GSD_theta], 
                                       thetaobs_se = est_sim[col_CONMIX_GSD_theta_se], 
                                       theta = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "conmix"])
  CONMIX_GSD_coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_CONMIX_GSD_theta]], 
                                                                       thetaobs_se = est_sim[[col_CONMIX_GSD_theta_se]])
  CONMIX_GSD_type1error_calc[i] <- type1error(est_sim[[col_CONMIX_GSD_mr_pval]])

  ## GBC additional metrics ----------------------------------------------------
  # IVW
  col_IVW_GBC_theta <- paste0("IVW_theta_sim_BMI_GBC_", format(sample_size, scientific = FALSE))
  col_IVW_GBC_theta_se <- paste0("IVW_theta_se_sim_BMI_GBC_", format(sample_size, scientific = FALSE))
  col_IVW_GBC_mr_pval <- paste0("IVW_mr_pval_BMI_GBC_", format(sample_size, scientific = FALSE))
  # calc
  IVW_GBC_coverage_calc[i] <- coverage(thetaobs = est_sim[col_IVW_GBC_theta], thetaobs_se = est_sim[col_IVW_GBC_theta_se], theta = est$estimate[est$mr_methods == "IVW"])
  IVW_GBC_coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_IVW_GBC_theta]], thetaobs_se = est_sim[[col_IVW_GSD_theta_se]])
  IVW_GBC_type1error_calc[i] <- type1error(est_sim[[col_IVW_GBC_mr_pval]])
  # MODE
  col_MODE_GBC_theta <- paste0("MODE_theta_sim_BMI_GBC_", format(sample_size, scientific = FALSE))
  col_MODE_GBC_theta_se <- paste0("MODE_theta_se_sim_BMI_GBC_", format(sample_size, scientific = FALSE))
  col_MODE_GBC_mr_pval <- paste0("MODE_mr_pval_BMI_GBC_", format(sample_size, scientific = FALSE))
  # calc
  MODE_GBC_coverage_calc[i] <- coverage(thetaobs = est_sim[col_MODE_GBC_theta], 
                                       thetaobs_se = est_sim[col_MODE_GBC_theta_se], 
                                       theta = est$estimate[est$mr_methods == "mode"])
  MODE_GBC_coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_MODE_GBC_theta]], 
                                                                       thetaobs_se = est_sim[[col_MODE_GBC_theta_se]])
  MODE_GBC_type1error_calc[i] <- type1error(est_sim[[col_MODE_GBC_mr_pval]])
  # CONMIX
  col_CONMIX_GBC_theta <- paste0("CONMIX_theta_sim_BMI_GBC_", format(sample_size, scientific = FALSE))
  col_CONMIX_GBC_theta_se <- paste0("CONMIX_theta_se_sim_BMI_GBC_", format(sample_size, scientific = FALSE))
  col_CONMIX_GBC_mr_pval <- paste0("CONMIX_mr_pval_BMI_GBC_", format(sample_size, scientific = FALSE))
  # calc
  CONMIX_GBC_coverage_calc[i] <- coverage(thetaobs = est_sim[col_CONMIX_GBC_theta], 
                                       thetaobs_se = est_sim[col_CONMIX_GBC_theta_se], 
                                       theta = est$estimate[est$mr_methods == "conmix"])
  CONMIX_GBC_coverage_bias_eliminated_calc[i] <- coverage_bias_eliminated(thetaobs = est_sim[[col_CONMIX_GBC_theta]], 
                                                                       thetaobs_se = est_sim[[col_CONMIX_GBC_theta_se]])
  CONMIX_GBC_type1error_calc[i] <- type1error(est_sim[[col_CONMIX_GBC_mr_pval]])  
}
```

```{r add-additional-metrics-to-df}
## GSD
IVW_GSD_performance_metrics <- IVW_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(IVW_GSD_coverage_calc, IVW_GSD_coverage_bias_eliminated_calc, IVW_GSD_type1error_calc)) %>% 
  rename(coverage = IVW_GSD_coverage_calc, 
         coverage_bias_eliminated = IVW_GSD_coverage_bias_eliminated_calc, 
         type1error = IVW_GSD_type1error_calc) %>% 
  as_tibble()
MODE_GSD_performance_metrics <- MODE_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(MODE_GSD_coverage_calc, MODE_GSD_coverage_bias_eliminated_calc, MODE_GSD_type1error_calc)) %>% 
  rename(coverage = MODE_GSD_coverage_calc, 
         coverage_bias_eliminated = MODE_GSD_coverage_bias_eliminated_calc, 
         type1error = MODE_GSD_type1error_calc) %>% 
  as_tibble()
CONMIX_GSD_performance_metrics <- CONMIX_GSD_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(CONMIX_GSD_coverage_calc, CONMIX_GSD_coverage_bias_eliminated_calc, CONMIX_GSD_type1error_calc)) %>% 
  rename(coverage = CONMIX_GSD_coverage_calc, 
         coverage_bias_eliminated = CONMIX_GSD_coverage_bias_eliminated_calc, 
         type1error = CONMIX_GSD_type1error_calc) %>% 
  as_tibble()

## GBC
IVW_GBC_performance_metrics <- IVW_GBC_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(IVW_GBC_coverage_calc, IVW_GBC_coverage_bias_eliminated_calc, IVW_GBC_type1error_calc)) %>% 
  rename(coverage = IVW_GBC_coverage_calc, 
         coverage_bias_eliminated = IVW_GBC_coverage_bias_eliminated_calc, 
         type1error = IVW_GBC_type1error_calc) %>% 
  as_tibble()
MODE_GBC_performance_metrics <- MODE_GBC_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(MODE_GBC_coverage_calc, MODE_GBC_coverage_bias_eliminated_calc, MODE_GBC_type1error_calc)) %>% 
  rename(coverage = MODE_GBC_coverage_calc, 
         coverage_bias_eliminated = MODE_GBC_coverage_bias_eliminated_calc, 
         type1error = MODE_GBC_type1error_calc) %>% 
  as_tibble()
CONMIX_GBC_performance_metrics <- CONMIX_GBC_performance_metrics %>% 
  select(N, everything()) %>% 
  cbind(data.frame(CONMIX_GBC_coverage_calc, CONMIX_GBC_coverage_bias_eliminated_calc, CONMIX_GBC_type1error_calc)) %>% 
  rename(coverage = CONMIX_GBC_coverage_calc, 
         coverage_bias_eliminated = CONMIX_GBC_coverage_bias_eliminated_calc, 
         type1error = CONMIX_GBC_type1error_calc) %>% 
  as_tibble()
```

```{r store-performance-metrics-csv}
## GSD
filename_IVW_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_IVW_GSD_performance_metrics_NSIM_", nsim, ".csv")
filename_MODE_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_MODE_GSD_performance_metrics_NSIM_", nsim, ".csv")
filename_CONMIX_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_CONMIX_GSD_performance_metrics_NSIM_", nsim, ".csv")
write.csv2(x = IVW_GSD_performance_metrics, file = filename_IVW_GSD_performance_metrics)
write.csv2(x = MODE_GSD_performance_metrics, file = filename_MODE_GSD_performance_metrics)
write.csv2(x = CONMIX_GSD_performance_metrics, file = filename_CONMIX_GSD_performance_metrics)

## GBC
filename_IVW_GBC_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_IVW_GBC_performance_metrics_NSIM_", nsim, ".csv")
filename_MODE_GBC_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_MODE_GBC_performance_metrics_NSIM_", nsim, ".csv")
filename_CONMIX_GBC_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_CONMIX_GBC_performance_metrics_NSIM_", nsim, ".csv")
write.csv2(x = IVW_GBC_performance_metrics, file = filename_IVW_GBC_performance_metrics)
write.csv2(x = MODE_GBC_performance_metrics, file = filename_MODE_GBC_performance_metrics)
write.csv2(x = CONMIX_GBC_performance_metrics, file = filename_CONMIX_GBC_performance_metrics)
```

## Performance Plots
